```{r setup, include=FALSE,message=FALSE,warning=FALSE}
# OPTIONS -----------------------------------------------
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message = FALSE)

# PACKAGES-----------------------------------------------
# Tutorial packages
library(vembedr)
library(skimr)
library(yarrr)
library(RColorBrewer)
library(GGally) 
library(tidyverse)
library(plotly)
library(readxl)
library(rvest)
library(biscale)
library(tidycensus)
library(cowplot)
library(units)
library(olsrr)

data("pirates", package = "yarrr")

```



# Confidence and Prediction Intervals

## What are they?

Essentially these are two different things:

**Confidence interval:** "Error bar" on the location of the regression line at any specific value of x, or "what is the uncertainty on the population mean of $y$, for a specific value of $x$?"

**Prediction interval:** Predicting the range of likely y-values for a new data-point, or "if you had to put a new dot on the scatterplot, what range of y values would it likely be found in

These are described in detail here:

-   <https://online.stat.psu.edu/stat462/node/125/>
-   <https://online.stat.psu.edu/stat462/node/126/>
-   <https://online.stat.psu.edu/stat462/node/127/>
-   <https://online.stat.psu.edu/stat462/node/128/>

In R, lets look at the pirate dataset

```{r}
#For our pirate weight/height dataset
lm.pirate <- lm(weight~height,data=pirates)
summary(lm.pirate)
```

## Calculating a confidence interval

**What are the AVERAGE WEIGHTS (and uncertainty on our estimate) of pirates whose heights are 150cm and 170cm?**

```{r}
# So we have the MODEL
lm.pirate <- lm(weight~height,data=pirates)


# a mini table of our new X-Values - you need the column name to be identical to your predictor
new.pirates <- data.frame(height=c(150,170))


# and the command
# predict (MODEL_NAME ,  NAME_OF_NEW_DATA,  TYPE_OF_INTERVAL, SIG LEVEL)
predict(lm.pirate,newdata=new.pirates,interval="confidence",level=0.95)

```

We are 95% certain that on average, the AVERAGE weight of pirates who are 150cm tall falls between 52.8 Kg and 53.74 Kg.

We are 95% certain that on average, the AVERAGE weight of pirates who are 170cm tall falls between 69.32 Kg and 69.80 Kg.

## Calculating a prediction interval

**A new pirate joins and her height is 160cm. What range of weights is she likely to have? with a significance level of 99%**

```{r}
# So we have the MODEL
lm.pirate <- lm(weight~height,data=pirates)


# a mini table of our new X-Values - you need the column name to be identical to your predictor
new.pirates <- data.frame(height=c(160))


# and the command
# predict (MODEL_NAME ,  NAME_OF_NEW_DATA,  TYPE_OF_INTERVAL, SIG LEVEL)
predict(lm.pirate,newdata=new.pirates,interval="predict",level=0.99)

```

Given our model, her weight is likely to be somewhere between 51.27 Kg and 71.56 Kg with 99% certainty.



